\documentclass{KPS_assignment}
% ---------For Persian------------
% \newcommand*{\name}{کیوان جمالی}
% \newcommand*{\id}{403209743}
% \newcommand*{\professor}{دکتر شفاهی}
% \newcommand*{\cdate}{2024/12/26}
% \newcommand*{\course}{درس (شماره)}
% \newcommand*{\assignment}{تمرین شماره1}
% ----------For English------------
\newcommand*{\name}{Keivan Jamali}
\newcommand*{\id}{403209743}
\newcommand*{\professor}{Dr. Shafahi}
\newcommand*{\cdate}{1405/02/24}
\newcommand*{\course}{Airport (20\_582)}
\newcommand*{\assignment}{Homework 3}
% ----------START------------------
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\begin{document}
\maketitle
\section{Problem}

The following data are given for passenger travel demand over a five-year period.

\begin{table}[!h]
\centering
\caption{Passenger Travel Demand Data}
\begin{tabular}{|c|c|c|}
\hline
\textbf{Fare per Passenger-Mile, $p$} &
\textbf{Travel Demand, $q$ ($10^6$ passenger-miles)} &
\textbf{Year, $t$} \\ \hline

0.30 & 639 & 1386 \\ \hline
0.30 & 698 & 1387 \\ \hline
0.30 & 762 & 1388 \\ \hline
0.30 & 828 & 1389 \\ \hline
0.30 & 904 & 1390 \\ \hline

\end{tabular}
\end{table}

\begin{enumerate}

\item Using regression analysis, estimate the travel demand volume for the year 1395.

\item Suppose that, due to a new regulation introduced in Farvardin 1391, the fare per passenger-mile decreases to $p = 0.24$. As a result, the travel demand in 1391 increases to $1{,}221{,}000{,}000$ passenger-miles.

Answer the following questions:

\begin{enumerate}
    \item Calculate the demand elasticity.
    
    \item Determine a linear demand function of the form:
    
    \[
    q = f(p)
    \]
    
    for the year 1391.
    
    \item Determine the maximum profit that the airport can obtain in 1391, assuming the total cost function is:
    
    \[
    TC = 100{,}000 + 80{,}000q
    \]
    
    \item Determine a demand function of the form:
    
    \[
    q = f(p,t)
    \]
    
    for the travel demand volume.
    
    \item What additional information would be necessary for designing the airport transportation system corresponding to the airports discussed in part (a)?
    
\end{enumerate}

\end{enumerate}

\subsection{solution to part a}

To estimate the travel demand for year 1395, a linear regression model is fitted in the form:

\[
q = a + b(t-80)
\]

where:

\begin{itemize}
    \item $q$ = travel demand ($10^6$ passenger-miles)
    \item $t$ = year
\end{itemize}

For simplicity, define:

\[
x=t-80
\]

Thus, the data become:

\[
(6,639), (7,698), (8,762), (9,828), (10,904)
\]

The required summations are:

\[
\sum x = 6+7+8+9+10 = 40
\]

\[
\sum q = 639+698+762+828+904 = 3831
\]

\[
\sum x^2 = 36+49+64+81+100 = 330
\]

\[
\sum xq =
6(639)+7(698)+8(762)+9(828)+10(904)
=31308
\]

and

\[
n=5
\]

The slope of the regression line is:

\[
b=
\frac{
n\sum xq-(\sum x)(\sum q)
}{
n\sum x^2-(\sum x)^2
}
\]

\[
b=
\frac{
5(31308)-40(3831)
}{
5(330)-40^2
}
=
\frac{
156540-153240
}{
1650-1600
}
=
\frac{3300}{50}
=66
\]

The intercept is:

\[
a=
\frac{
\sum q-b\sum x
}{n}
\]

\[
a=
\frac{
3831-66(40)
}{5}
=
\frac{
3831-2640
}{5}
=
238.2
\]

Therefore, the regression equation becomes:

\[
\boxed{
q = 238.2 + 66(t-80)
}
\]

For year 1395:

\[
t-80 = 15
\]

Thus:

\[
q_{1395}=238.2+66(15)
\]

\[
q_{1395}=238.2+990
\]

\[
\boxed{
q_{1395}=1228.2
}
\]

Therefore, the estimated travel demand for year 1395 is:

\[
\boxed{
1228.2\times 10^6
\text{ passenger-miles}
}
\]



\subsection{solution to part b}

\subsubsection{Demand Elasticity}

From part (a), the estimated demand for year 1391 at the original fare $p=0.30$ is:

\[
q_1 = 238.2+66(11)=964.2
\]

After the fare reduction:

\[
p_2=0.24
\]

and the new demand becomes:

\[
q_2=1221
\]

Using the arc elasticity formula:

\[
E=
\frac{\Delta q}{\Delta p}
\cdot
\frac{\bar p}{\bar q}
\]

First compute the changes and averages:

\[
\Delta q = 1221-964.2 = 256.8
\]

\[
\Delta p = 0.24-0.30 = -0.06
\]

\[
\bar p = \frac{0.30+0.24}{2}=0.27
\]

\[
\bar q = \frac{964.2+1221}{2}=1092.6
\]

Therefore:

\[
E=
\frac{256.8}{-0.06}
\cdot
\frac{0.27}{1092.6}
\]

\[
\boxed{
E \approx -1.06
}
\]

The negative sign indicates that demand increases when price decreases.



\subsubsection{Linear Demand Function for Year 1391}

Using the two points:

\[
(p,q)=(0.30,964.2)
\]

and

\[
(p,q)=(0.24,1221)
\]

Assume a linear demand function:

\[
q=mp+c
\]

The slope is:

\[
m=
\frac{1221-964.2}{0.24-0.30}
=
\frac{256.8}{-0.06}
=-4280
\]

Thus:

\[
q=-4280p+c
\]

Using point $(0.30,964.2)$:

\[
964.2=-4280(0.30)+c
\]

\[
964.2=-1284+c
\]

\[
c=2248.2
\]

Therefore, the demand function becomes:

\[
\boxed{
q=2248.2-4280p
}
\]



\subsubsection{Maximum Profit in 1391}

From the demand function:

\[
q=2248.2-4280p
\]

Express price in terms of demand:

\[
p(q)=\frac{2248.2-q}{4280}
\]

Revenue is:

\[
R=10^6pq
\]

Thus:

\[
R=
10^6
\left(
\frac{2248.2-q}{4280}
\right)
q
\]

The total cost function is given as:

\[
TC=100000+80000q
\]

Profit is:

\[
\Pi(q)=R-TC
\]

Therefore:

\[
\Pi(q)=
10^6
\left(
\frac{2248.2-q}{4280}
\right)q
-100000
-80000q
\]

Simplifying:

\[
\Pi(q)=
-233.64486q^2
+445280.3738q
-100000
\]

To maximize profit:

\[
\frac{d\Pi}{dq}=0
\]

Hence:

\[
-467.28972q+445280.3738=0
\]

Solving:

\[
\boxed{
q^*=952.9
}
\]

Substituting into the demand equation:

\[
p^*=
\frac{2248.2-952.9}{4280}
\]

\[
\boxed{
p^*\approx0.3026
}
\]

Finally:

\[
\Pi_{\max}
=
10^6
\left(
\frac{2248.2-952.9}{4280}
\right)
(952.9)
-100000
-80000(952.9)
\]

\[
\boxed{
\Pi_{\max}\approx2.12\times10^8
}
\]



\subsubsection{Demand Function of the Form $q=f(p,t)$}

Assume a linear demand model:

\[
q=A+B(t-80)+Cp
\]

From part (a), the time trend coefficient is:

\[
B=66
\]

Thus:

\[
q=A+66(t-80)+Cp
\]

Using the two observations for year 1391:

\[
964.2=A+66(11)+0.30C
\]

\[
1221=A+66(11)+0.24C
\]

Since:

\[
66(11)=726
\]

the equations become:

\[
964.2=A+726+0.30C
\]

\[
1221=A+726+0.24C
\]

Subtracting the equations:

\[
256.8=-0.06C
\]

\[
C=-4280
\]

Substituting back:

\[
964.2=A+726-1284
\]

\[
A=1522.2
\]

Therefore, the final demand model becomes:

\[
\boxed{
q=1522.2+66(t-80)-4280p
}
\]



\subsubsection{Additional Information Required for Airport Transportation System Design}

To design the airport transportation system, annual passenger demand alone is not sufficient. Additional information is required, including:

\begin{itemize}
    \item Peak-hour passenger demand
    \item Seasonal demand variations
    \item Origin-destination passenger distribution
    \item Passenger type (domestic, international, transfer)
    \item Aircraft size and fleet mix
    \item Passenger load factors
    \item Desired level of service
\end{itemize}

These data are necessary for proper design of airport terminals, runways, parking areas, and transportation facilities.

\end{document}

