\documentclass{KPS_assignment}
% ---------For Persian------------
%\newcommand*{\name}{کیوان جمالی}
%\newcommand*{\id}{403209743}
%\newcommand*{\professor}{دکتر شفاهی}
%\newcommand*{\cdate}{2024/12/26}
%\newcommand*{\course}{درس (شماره)}
%\newcommand*{\assignment}{تمرین شماره1}
% ----------For English------------
\newcommand*{\name}{Keivan Jamali}
\newcommand*{\id}{403209743}
\newcommand*{\professor}{Prof. Amini}
\newcommand*{\cdate}{1404/09/18}
\newcommand*{\course}{Advanced Traffic (20--551)}
\newcommand*{\assignment}{Class Project Part 5}
% ----------START------------------
\begin{document}
\maketitle
\section*{Part 5: Simulation Engine \& Data Logging}

\textbf{Goals:}
\begin{enumerate}
\item Use \texttt{SimPy} or a custom loop to implement the simulation engine.
\item Read the demand file and generate vehicles correctly.
\item Build the simulation loop and collect data.
\end{enumerate}

\subsection*{Tasks}
\begin{enumerate}
    \item Implement a simulation engine (using \texttt{SimPy} or a custom loop).
    \item Generate vehicles from demand data and move them according to the defined logic.
    \item Log vehicle positions and states to a \texttt{DataFrame}.
\end{enumerate}

\subsection*{Output}
\begin{enumerate}
\item Implement \texttt{Engine.py} to run the simulation.
\item Modify Python modules as needed to integrate with \texttt{Engine.py}.
\item Provide brief documentation in all files and include a \texttt{README.md}.
\item Present the code and answer questions.
\item Provide the log file (CSV).
\end{enumerate}

\subsection*{Time}
10 days (1404-09-28)

\subsection*{Grade Weight}
30\% total for Parts 2--4 [Part 2: 15\%, Part 3: 5\%, Part 4: 10\%].\\
- If there are problems in the vehicles or network, you will lose a portion of the 20\%.\\
- If there are problems in the traffic light logic, you will lose a portion of the 10\%.\\
- If there are problems in the Engine, you will likely lose the 10\% for Part 4.
\end{document}