\documentclass{KPS_assignment}
% ---------For Persian------------
%\newcommand*{\name}{کیوان جمالی}
%\newcommand*{\id}{403209743}
%\newcommand*{\professor}{دکتر شفاهی}
%\newcommand*{\cdate}{2024/12/26}
%\newcommand*{\course}{درس (شماره)}
%\newcommand*{\assignment}{تمرین شماره1}
% ----------For English------------
\newcommand*{\name}{Keivan Jamali}
\newcommand*{\id}{403209743}
\newcommand*{\professor}{Prof. Amini}
\newcommand*{\cdate}{1404/08/27}
\newcommand*{\course}{Advanced Traffic (20--551)}
\newcommand*{\assignment}{Class Project Part 3}
% ----------START------------------
\begin{document}
\maketitle
\section*{Part 3: Object-Oriented Programming (OOP) for Traffic Elements}

\textbf{Goals:}
\begin{enumerate}
\item Apply object-oriented programming (OOP).
\item Define network objects.
\item Define agents and their capabilities.
\end{enumerate}

\subsection*{Tasks}
\begin{enumerate}
    \item Implement classes (e.g., \texttt{Lane} and \texttt{Intersection}).
    \item Each class should expose relevant functionality (e.g., traffic signal control) and be able to store state/data.
    \item Vehicles should travel along lanes and interact at intersections.
\end{enumerate}

\subsection*{Outputs}
\begin{enumerate}
\item One or more Python files implementing the features described above.
\item A brief report about the code (inline documentation in all files and a \texttt{README.md} file).
\item Present the code and answer questions.
\end{enumerate}

\subsection*{Time}
1 week (1404-09-04)

\subsection*{Grade Weight}
5\%. In this part, you cannot fully evaluate whether the code is effective. Most of the points for this part will be combined with other parts. The current score evaluates only the structure of your classes and how well they are designed for future extension.

\end{document}